---
# The YAML header specifies several settings for the survey but is not required.
# A full list of settings can be found under _survey/settings.yml directory.

theme-settings:
  theme: default
  barposition: top
  footer-left: "Made with [surveydown](https://surveydown.org)"
  footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/template_questions_yml)'

survey-settings:
  mode: preview
  show-previous: false
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-required: false
---

```{r}
library(surveydown)
```

--- welcome

# Template - Questions Defined with YAML

This is a showcase of defining questions with a `questions.yml` file.

The `sd_question()` allows a `yml` argument default to `"questions.yml"`. If you have such file in your project root folder, you can use it to support your question definition.

You can also change to other file name or directory and define questions like this:

```{r}
#| eval: false
#| echo: true
sd_question(
  id = "your_question_id",
  yml = "folder_name/file_name.yml"
)
```

Please click on the "Next" button to see the demo questions.

--- question_types

# Question types

This page showcases the different types of question supported by `{surveydown}`. They are all defined in `"questions.yml"` and called by `sd_question(id = "question_id")`.

The question types are:

  - `text`: Single line open text input.
  - `textarea`: Multiple line open text input.
  - `numeric`: Single line numeric text input.
  - `mc`: Multiple choice with a single select option (radio buttons).
  - `mc_buttons`: Same as `mc` but as a "button" style instead of radio buttons.
  - `mc_multiple`: Multiple choice with mutliple select options (check boxes).
  - `mc_multiple_buttons`: Same as `mc_multiple` but as a "button" style instead of check boxes.
  - `mc_image`: Same as `mc` but each option is a clickable image card (single select).
  - `mc_multiple_image`: Same as `mc_multiple` but each option is a clickable image card (multiple select).
  - `select`: Select a choice from a dropdown menu.
  - `slider`: Slider to select discrete categories or continuous numbers.
  - `slider_numeric`: Slider to select a single number or a numeric range.
  - `date`: Select a date from a calendar widget.
  - `daterange`: Select two dates from calendar widgets (e.g. begin and end dates).
  - `matrix`: Several questions with same list of options. Each question is in fact an `mc` question.
  - `matrix_multiple`: Same as `matrix` but each row allows multiple selections. Each question is in fact an `mc_multiple` question.

#### Use `type = 'text'` to specify a text input type question:

```{r}
sd_question("silly_word")
```

#### Use `type = 'textarea'` to specify a textarea input type question:

```{r}
sd_question("silly_paragraph")
```

#### Use `type = 'numeric'` to specify a numeric input type:

```{r}
sd_question("age")
```

#### Use `type = 'mc'` to specify a multiple choice type question with a single choice option:

```{r}
sd_question("artist")
```

#### Use `type = 'mc_buttons'` to generate the button version of `mc`:

```{r}
sd_question("fruit")
```

#### Use `type = 'mc_multiple'` to specify a multiple choice type question with multiple selection enabled:

```{r}
sd_question("swift")
```

#### Use `type = 'mc_multiple_buttons'` to generate the button version of `mc_multiple`:

```{r}
sd_question("michael_jackson")
```

#### Use `type = 'mc_image'` to specify a single choice question with image options:

Each option is a clickable image card. Image paths are **not** stored in `questions.yml`, so they are passed with the `image` argument of `sd_question()` (one image path or URL per option, in the same order as the options). Image paths resolve against the survey's `images/` folder. When the options are **named** in the YAML, the names are shown as text captions beneath each image.

```{r}
sd_question(
  "apple_image",
  image = c(
    "images/fuji.jpg",
    "images/pink_lady.jpg",
    "images/honeycrisp.jpg"
  )
)
```

#### Use `type = 'mc_multiple_image'` to specify a multiple choice question with image options:

Same as `mc_image` but multiple cards can be selected. The `image` argument is again passed in `sd_question()`.

```{r}
sd_question(
  "apple_buy",
  image = c(
    "images/fuji.jpg",
    "images/pink_lady.jpg",
    "images/honeycrisp.jpg"
  )
)
```

#### Use `type = 'select'` to specify a drop down select type question:

```{r}
sd_question("education")
```

#### Use `type = 'slider'` to specify a slider input type:

```{r}
sd_question("climate_care")
```

#### Use `type = 'slider_numeric'` to specify a numeric slider input type:

```{r}
sd_question("slider_single_val")
```

#### `type = 'slider_numeric'` can also be used for range selection (2 numerics):

```{r}
sd_question("slider_range")
```

#### Use `type = 'date'` to specify a date input type:

```{r}
sd_question("dob")
```

#### Use `type = 'daterange'` to specify a daterange input type:

```{r}
sd_question("hs_date")
```

#### Use `type = 'matrix'` to specify a matrix input type:

```{r}
sd_question("car_preference")
```

#### Use `type = 'matrix_multiple'` to specify a matrix input where each row allows multiple selections:

Same as `matrix`, but each row uses check boxes instead of radio buttons, so respondents can select more than one option per row. Each row is stored as its own column, with multiple selections pipe-joined (e.g. `"fast|cheap"`).

```{r}
sd_question("vehicle_features")
```

--- end

## Thanks for taking our survey!

```{r}
sd_close()
```